Personalization and probabilities: the expression of propensities in online grocery shopping

### 2017-07-31 reconstruction.rmd
updating slides

The main argument of the paper concerns how  probability operates in Big Data situations. While calculations of probability have  long-standing importance in many settings (insurance, medicine, experimental and field sciences, operations research, risk analysis, engineering design, public health,  economic modelling, etc.), probabilities have taken on a much thicker situational texture on digital platforms associated with the web and social media. In recent research and opinion on data practice, personalization has been seen as the linchpin of predictive modelling.  Big data discourse in its promissory mode  attributes potency to personalization: 'most important, using big data we hope to identify specific individuals rather than groups' [@Mayer-Schonberger_2013]. Similarly, Joseph Turow and co-authors conclude in their critical account of the transformation of retail space: 'through it all, knowingly and not, and away from the spotlights of fierce social debate, retailers are encouraging daily routines that accept data-driven personalization as a centrifugal public' [@Turow_2015, 476]. Analysis of internet filter bubbles and the growth of predictive platforms in industry and government make similar points [@Pariser_2011; @ONeil_2016].

>>>>

The main argument of the paper concerns how  probability operates in Big Data situations. While calculations of probability have  long-standing importance in many settings (insurance, medicine, experimental and field sciences, operations research, risk analysis, engineering design, public health,  economic modelling, etc.), probabilities have taken on a much thicker situational texture on digital platforms associated with the web and social media. In recent research and opinion on data practice, personalization has been seen as the linchpin of predictive modelling.  Big data discourse in its promissory mode  attributes potency to personalization: 'most important, using big data we hope to identify specific individuals rather than groups' [@Mayer-Schonberger_2013]. Similarly, Joseph Turow and co-authors conclude in their critical account of the transformation of retail space: 'through it all, knowingly and not, and away from the spotlights of fierce social debate, retailers are encouraging daily routines that accept data-driven personalization as a centrifugal public' [@Turow_2015, 476]. Analysis of internet filter bubbles and the growth of predictive platforms in industry and government make similar arguments [@Pariser_2011; @ONeil_2016a].
